The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching

### 2017-03-25 article.tex
Another small type (rev #2)

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates can optionally identify
  perspective projections, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently consider distinct can be merged
  (Figure~\ref{fig:stereoprojections}).  The perception is based on an  algorithm briefly  
  described by~\cite{Karapetyan2015}.

>>>>

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates can optionally identify
  perspective projections, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently considered distinct can be merged
  (Figure~\ref{fig:stereoprojections}).  The perception is based on an  algorithm briefly  
  described by~\cite{Karapetyan2015}.
